Continuously Generalizing Buildings to Built-up Areas\\ by Aggregating and Growing

### 2017-09-22 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
a little improvement

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on
C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1.
The offsetting function and clipping function are from library \textsc{Clipper} 
of \citet{Johnson2014}.
The offsetting function realizes 
our operations of buffering, dilating, eroding, and merging.
An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
\fig\ref{fig:Data} shows our testing data, 
which is from the French Mapping Agency (IGN).
The data is at scale $1:15{,}000$, which means $M_\mathrm{s}=15{,}000$.
It represents the buildings of four towns (communes in French), 
i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
in the Pyr\'en\'ees-Atlantiques department, south-western France.

@@

Our program took $93.6\,\mathrm{s}$ 
to compute the goal shapes of the built-up areas.
\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
The $56$ built-up areas have $2{,}095$ edges before line simplification.
Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
In comparison, there are $1{,}597$ edges left if we simplify using
the Douglas--Peucker algorithm.

We produced a sequence of $10$ maps, i.e., $t \in \{0.1, 0.2, \dots, 1\}$.
This production cost $668.2\,\mathrm{s}$ in total.
We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
the marked region in \fig\ref{fig:GoalShape}.
We counted the numbers of buildings in our results,
and compared our numbers to the numbers calculated by T\"opfer's radical law
(see \fig\ref{fig:BuilidngNumber}).
We have unexaggerated-area symbols, 
so for \eq2 of \citet{Topfer1966}, we used $C_\mathrm{b2}$ and $C_\mathrm{z3}$.
As a result, we computed the number according to
\[
n_t=n_\mathrm{s}\frac{M_\mathrm{s}}{M_t},
\]
where $n_s=2{,}590$ is the number of buildings on start map
and $n_t$ is the number of buildings on a map at scale $1:M_t$.
According to \fig\ref{fig:BuilidngNumber}, our numbers decrease faster than 
the numbers from the radical law.
It seems that our result supports the fractal law proposed by \citet{Jiang2015}.

\begin{figure}[tb]
	\centering
	\begin{tikzpicture}[]
	\begin{axis}[
	height=5cm,
	width= \linewidth-0.1cm,
	axis lines = left,
	%	axis x line=center,
	%	axis y line=left,
	xtick={0.1,0.2,...,1},
	ytick={500,1000,...,3000},
	xlabel={$t$},
	ylabel={number of buildings},
	xlabel style={below right},
	%	ylabel style={at={(axis description cs:0,1.1)},rotate=270,anchor=north},
	xlabel style={at={(axis description cs:1,0)},anchor=north},
	%	ylabel style={above left},
	xmin=0,
	xmax=1.1,
	ymin=0,
	ymax=3200,
	cycle list name=black white,
	]
	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
	\addplot+  coordinates {
		(0,2590)
		(0.1,1963)
		(0.2,758)
		(0.3,304)
		(0.4,177)
		(0.5,122)
		(0.6,92)
		(0.7,73)
		(0.8,66)
		(0.9,59)
		(1,56)		
	};
	\legend{\quad radical law, \quad our results}
	\end{axis}
	\end{tikzpicture}
	\caption{A comparison of the numbers of building between our results and 
		T\"opfer's radical law.}
	\label{fig:BuilidngNumber}
\end{figure}

\fig\ref{fig:ExperimentalComparison} shows a comparison of 
our result at time $t=1$
and the data from IGN at scale $1:50{,}000$.
No small buildings are removed in our result or the IGN data.
The boundaries of our built-up areas are more straight than that of IGN data, 
where we have $1{,}135$ edges while the data has $4{,}968$ edges.
From this perspective, we would say that our result is 
more reasonable than the existing data.
A questionnaire, however, is needed to make a more convincing comparison.

@@

%The area on start map is $some number\,\text{mm}^2$.
%Our area on map is $some number\,\text{mm}^2$.
%According to \eq4 of paper \citet{Topfer1966}, 
%the area on map should be $some number\,\text{mm}^2$

@@

It is always interesting to know what is the quantity we should keep on a map.
We compared the number of buildings between our results and the calculated 
numbers from T\"opfer's radical law.
It turned out that our numbers decreased too fast.
We may also take into account the fractal law of \citet{Jiang2015}.
Another interesting problem is to compare the area of the buildings.

Eventually, our result is a set of settlement boundaries. An interesting 
problem is to compare our method with \citet{Chaudhry2008}.

>>>>

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on
C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1. 
The code is available in open source on 
Github\footnote{\url{https://github.com/IGNF/Continuous-Generalisation}}.
The offsetting function and clipping function 
are available from library \textsc{Clipper} of \citet{Johnson2014}.
The offsetting function is used for the buffering, dilation, erodion, and merge operations.
An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
Our testing data is extracted from a dataset produced 
by the French Mapping Agency (IGN);
see \fig\ref{fig:Data}.
The data is at scale $1:15{,}000$, which means $M_\mathrm{s}=15{,}000$.
It represents the buildings of four towns, 
i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
in the Pyr\'en\'ees-Atlantiques county, south-western France.
IGN also stores a dataset at scale $1:50{,}000$.
This dataset was basically obtained from the data at scale $1:15{,}000$ 
by buffering with distance $25\,\mathrm{m}$,
where sometimes distance $50\,\mathrm{m}$ was also used
in order to identify towns.
A restriction for the town from \citet{Boffet2000} is that 
the longest edge in an MST of the buildings 
should be shorter than $100\,\mathrm{m}$.

@@

Our program took $93.6\,\mathrm{s}$ 
to compute the goal shapes of the built-up areas.
\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
The $56$ built-up areas have $2{,}095$ edges before line simplification.
Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
In comparison, there are $1{,}597$ edges left when we simplified using
the Douglas--Peucker algorithm.

We produced a sequence of $10$ maps, i.e., $t \in \{0.1, 0.2, \dots, 1\}$.
This production costs $668.2\,\mathrm{s}$ in total.
We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
the marked region in \fig\ref{fig:GoalShape}.
We counted the numbers of buildings in our results,
and compared our numbers to the numbers calculated by T\"opfer's radical law
(see \fig\ref{fig:BuilidngNumber}).
We have unexaggerated-area symbols, 
so for \eq2 of \citet{Topfer1966} we used $C_\mathrm{b2}$ and $C_\mathrm{z3}$.
As a result, we computed the numbers according to
\[
n_t=n_\mathrm{s}\frac{M_\mathrm{s}}{M_t},
\]
where $n_s=2{,}590$ is the number of buildings on start map
and $n_t$ is the number of buildings on a map at scale $1:M_t$.
According to \fig\ref{fig:BuilidngNumber}, our numbers decrease faster than 
the numbers from the radical law.
It seems that our result supports the fractal law proposed by \citet{Jiang2015}.

\begin{figure}[tb]
	\centering
	\begin{tikzpicture}[]
	\begin{axis}[
	height=5cm,
	width= \linewidth-0.1cm,
	axis lines = left,
	%	axis x line=center,
	%	axis y line=left,
	xtick={0.1,0.2,...,1},
	ytick={500,1000,...,3000},
	xlabel={$t$},
	ylabel={number of buildings},
	xlabel style={below right},
	%	ylabel style={at={(axis description cs:0,1.1)},rotate=270,anchor=north},
	xlabel style={at={(axis description cs:1,0)},anchor=north},
	%	ylabel style={above left},
	xmin=0,
	xmax=1.1,
	ymin=0,
	ymax=3200,
	cycle list name=black white,
	]
	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
%	\addplot+ [domain=0:1,samples=11] {2590* (15/(15+35* x))^1.5};
	\addplot+  coordinates {
		(0,2590)
		(0.1,1963)
		(0.2,758)
		(0.3,304)
		(0.4,177)
		(0.5,122)
		(0.6,92)
		(0.7,73)
		(0.8,66)
		(0.9,59)
		(1,56)		
	};
	\legend{\quad radical law, \quad our results}
	\end{axis}
	\end{tikzpicture}
	\caption{A comparison of the numbers of building between our results and 
		T\"opfer's radical law.}
	\label{fig:BuilidngNumber}
\end{figure}

\fig\ref{fig:ExperimentalComparison} shows a comparison of 
our result at time $t=1$
and the data at scale $1:50{,}000$.
No small building is removed in our result or the existing data.
The boundaries of our built-up areas are more straight than that of IGN data, 
where we have $1{,}135$ edges while the data has $4{,}968$ edges.
From this perspective, we would say that our result is 
more reasonable than the existing data.
A questionnaire, however, is needed to make a more convincing comparison.

@@

@@

It is always interesting to know what is the quantity we should keep on a map.
We compared the numbers of buildings of our results, and it is consistent with 
the fractal law from \citet{Jiang2015}.
Another interesting problem is to compare the area of the buildings.
Eventually, our result is a set of settlement boundaries. An interesting 
problem is to compare our method with \citet{Chaudhry2008}.
Our method is supposed to provide a smooth transition between representations 
with individual buildings and representations with built-up areas, but the only 
way to verify that smoothness is achieved is to carry out a user survey where 
our approach is compared to non continuous generalization approaches.
